SPARQL on the open, decentralised Web

### 2016-06-02 dissertation/introdefhistory.tex
Add the working ontologist book
point out beliefs

One such vision is the article by Berners-Lee, Hendler and Lassila in
Scientific American 2001\cite{berners2001semantic}, but it does not attempt such an
operational definition. Neither \cite{semwebroadmap} nor \cite{berners2000weaving} contain
such definitions. However, it is clear that an essential
characteristic of the Web, and by extension, the Semantic Web, is its
\emph{universality} and therefore, any actor should be as free as
possible to adapt it to their visions and needs. A pursuit of a
definition of the term ``Semantic Web'' would require a philosophical
treatment which would be beyond the scope of this thesis, and even
with that, may not be a fruitful exercise from a technical
perspective.

@@

>>>>

One such vision is the article by Berners-Lee, Hendler and Lassila in
Scientific American 2001\cite{berners2001semantic}, but it does not attempt such an
operational definition. Neither \cite{semwebroadmap},
\cite{berners2000weaving} nor \cite{Allemang:2008:SWW:1386668} contain
such definitions. However, it is clear that an essential
characteristic of the Web, and by extension, the Semantic Web, is its
\emph{universality} and therefore, any actor should be as free as
possible to adapt it to their visions and needs. A pursuit of a
definition of the term ``Semantic Web'' would require a philosophical
treatment which would be beyond the scope of this thesis, and even
with that, may not be a fruitful exercise from a technical
perspective.

@@

Lastly, while the discussion in Section~\ref{sec:conphil} should make
clear that I think that there are epistemological problems underneath
the entire field of study, i.e. there is reason to question the
validity of any result, there are invariably certain statements that
have a particularly weak foundation, especially in the motivation. I
shall attempt to be careful to use the term ``belief'' to qualify such
statements.
